---
title: "Ch15_Functions"
author: "Sam Csik"
date: "4/16/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Exercises pg.273 (19.2.1)

1. Why is `TRUE` not a parameter to `rescale01()`? What would happen if x contained a single missing value, and `na.rm` was FALSE?

2. In the second variant of `rescale01()`, infinite values are left unchanged. Rewrite `rescale01()` so that `-Inf` is mapped to 0, and `Inf` is mapped to 1.

3. Practice turning the following code snippets into functions. Think about what each function does. What would you call it? How many arguments does it need? Can you rewrite it to be more expressive or less duplicative?
```{r}
mean(is.na(x))

x / sum(x, na.rm = TRUE)

sd(x, na.rm = TRUE) / mean(x, na.rm = TRUE)
```

4. Follow http://nicercode.github.io/intro/writing-functions.html to write your own functions to compute the variance and skew of a numeric vector.

5. Write `both_na()`, a function that takes two vectors of the same length and returns the number of positions that have an NA in both vectors.

6. What do the following functions do? Why are they useful even though they are so short?
```{r}
is_directory <- function(x) file.info(x)$isdir
is_readable <- function(x) file.access(x, 4) == 0
```

7. Read the complete lyrics to “Little Bunny Foo Foo”. There’s a lot of duplication in this song. Extend the initial piping example to recreate the complete song, and use functions to reduce the duplication.

### Exercises pg. 276 (19.3.1)

1. Read the source code for each of the following three functions, puzzle out what they do, and then brainstorm better names.
```{r}
f1 <- function(string, prefix) {
  substr(string, 1, nchar(prefix)) == prefix
}
f2 <- function(x) {
  if (length(x) <= 1) return(NULL)
  x[-length(x)]
}
f3 <- function(x, y) {
  rep(y, length.out = length(x))
}
```

2. Take a function that you’ve written recently and spend 5 minutes brainstorming a better name for it and its arguments.

3. Compare and contrast `rnorm()` and `MASS::mvrnorm()`. How could you make them more consistent?

4. Make a case for why `norm_r()`, `norm_d()` etc would be better than `rnorm()`, `dnorm()`. Make a case for the opposite.

### Exercises pg. 279 (19.4.4)

1. What’s the difference between `if` and `ifelse()`? Carefully read the help and construct three examples that illustrate the key differences.

2. Write a greeting function that says “good morning”, “good afternoon”, or “good evening”, depending on the time of day. (Hint: use a time argument that defaults to `lubridate::now()`. That will make it easier to test your function.)

3. Implement a fizzbuzz function. It takes a single number as input. If the number is divisible by three, it returns “fizz”. If it’s divisible by five it returns “buzz”. If it’s divisible by three and five, it returns “fizzbuzz”. Otherwise, it returns the number. Make sure you first write working code before you create the function.

4. How could you use `cut()` to simplify this set of nested if-else statements?
```{r}
if (temp <= 0) {
  "freezing"
} else if (temp <= 10) {
  "cold"
} else if (temp <= 20) {
  "cool"
} else if (temp <= 30) {
  "warm"
} else {
  "hot"
}
```
How would you change the call to `cut()` if I’d used `<`instead of `<=`? What is the other chief advantage of `cut()` for this problem? (Hint: what happens if you have many values in temp?)

5. What happens if you use `switch(` with numeric values?

6. What does this `switch()` call do? What happens if x is “e”?
```{r}
switch(x, 
  a = ,
  b = "ab",
  c = ,
  d = "cd"
)
```
Experiment, then carefully read the documentation.

### Exercises pg. 285 (19.5.5)

1. What does `commas(letters, collapse = "-")` do? Why?

2. It’d be nice if you could supply multiple characters to the pad argument, e.g. `rule("Title", pad = "-+")`. Why doesn’t this currently work? How could you fix it?

3. What does the trim argument to `mean()` do? When might you use it?

4. The default value for the method argument to `cor()` is `c("pearson", "kendall", "spearman")`. What does that mean? What value is used by default?
