---
title: "Ch17_Interation_with_purrr"
author: "Sam Csik"
date: "4/16/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Exercises pg. 316  (21.2.1)

1. Write for loops to:

  a. Compute the mean of every column in mtcars.
  b. Determine the type of each column in `nycflights13::flights`.
  c. Compute the number of unique values in each column of `iris`.
  d, Generate 10 random normals for each of `μ = -10, 0, 10, and 100`

Think about the output, sequence, and body before you start writing the loop.

2. Eliminate the for loop in each of the following examples by taking advantage of an existing function that works with vectors:
```{r}
out <- ""
for (x in letters) {
  out <- stringr::str_c(out, x)
}

x <- sample(100)
sd <- 0
for (i in seq_along(x)) {
  sd <- sd + (x[i] - mean(x)) ^ 2
}
sd <- sqrt(sd / (length(x) - 1))

x <- runif(100)
out <- vector("numeric", length(x))
out[1] <- x[1]
for (i in 2:length(x)) {
  out[i] <- out[i - 1] + x[i]
}
```

3. Combine your function writing and for loop skills:

  a. Write a for loop that prints() the lyrics to the children’s song “Alice the camel”.
  b. Convert the nursery rhyme “ten in the bed” to a function. Generalise it to any number of people in any sleeping structure.
  c. Convert the song “99 bottles of beer on the wall” to a function. Generalise to any number of any vessel containing any liquid on any surface.

4. It’s common to see for loops that don’t preallocate the output and instead increase the length of a vector at each step:
```{r}
output <- vector("integer", 0)
for (i in seq_along(x)) {
  output <- c(output, lengths(x[[i]]))
}
output
```
How does this affect performance? Design and execute an experiment.

### Exercises pg. 321 (21.3.5)

1. Imagine you have a directory full of CSV files that you want to read in. You have their paths in a vector, `files <- dir("data/", pattern = "\\.csv$", full.names = TRUE)`, and now want to read each one with `read_csv()`. Write the for loop that will load them into a single data frame.

2. What happens if you use for `(nm in names(x))` and x has no names? What if only some of the elements are named? What if the names are not unique?

3. Write a function that prints the mean of each numeric column in a data frame, along with its name. For example,   `show_mean(iris)` would print:
```{r}
show_mean(iris)
#> Sepal.Length: 5.84
#> Sepal.Width:  3.06
#> Petal.Length: 3.76
#> Petal.Width:  1.20
```
(Extra challenge: what function did I use to make sure that the numbers lined up nicely, even though the variable names had different lengths?)

4. What does this code do? How does it work?
```{r}
trans <- list( 
  disp = function(x) x * 0.0163871,
  am = function(x) {
    factor(x, labels = c("auto", "manual"))
  }
)
for (var in names(trans)) {
  mtcars[[var]] <- trans[[var]](mtcars[[var]])
}
```

### Exercises pg. 324 (21.4.1)

1. Read the documentation for `apply()`. In the 2d case, what two for loops does it generalise?

2. Adapt `col_summary()` so that it only applies to numeric columns You might want to start with an `is_numeric()` function that returns a logical vector that has a TRUE corresponding to each numeric column.

### Exercises pg. 328 (21.5.3)

1. Write code that uses one of the map functions to:

  a. Compute the mean of every column in mtcars.
  b. Determine the type of each column in nycflights13::flights.
  c. Compute the number of unique values in each column of iris.
  d. Generate 10 random normals for each of `μ = -10, 0, 10, and 100`

2. How can you create a single vector that for each column in a data frame indicates whether or not it’s a factor?

3. What happens when you use the map functions on vectors that aren’t lists? What does `map(1:5, runif)` do? Why?

4. What does `map(-2:2, rnorm, n = 5)` do? Why? What does `map_dbl(-2:2, rnorm, n = 5)` do? Why?

5. Rewrite `map(x, function(df) lm(mpg ~ wt, data = df))` to eliminate the anonymous function.

### Exercises pg. 328 (21.9.3)

1. Implement your own version of `every()` using a for loop. Compare it with `purrr::every()`. What does purrr’s version do that your version doesn’t?

2. Create an enhanced `col_summary()` that applies a summary function to every numeric column in a data frame.

3. A possible base R equivalent of `col_summary()` is:
```{r}
col_sum3 <- function(df, f) {
  is_num <- sapply(df, is.numeric)
  df_num <- df[, is_num]

  sapply(df_num, f)
}
```

But it has a number of bugs as illustrated with the following inputs:
```{r}
df <- tibble(
  x = 1:3, 
  y = 3:1,
  z = c("a", "b", "c")
)
# OK
col_sum3(df, mean)
# Has problems: don't always return numeric vector
col_sum3(df[1:2], mean)
col_sum3(df[1], mean)
col_sum3(df[0], mean)
```
What causes the bugs?