---
title: "Ch1_Data_Visualization"
author: "Sam Csik"
date: "4/9/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Load required packages
```{r}
library(tidyverse)
```

### Exercises pg. 6

1. Run ggplot(data = mpg). What do you see?
```{r}
ggplot(data = mpg)
```
-> *Nothing! There is not a geom_ associated with it.*

2. How many rows are in mpg? How many columns?
```{r}
nrow(mpg) # 234
ncol(mpg) # 11
```

3. What does the drv variable describe? Read the help for ?mpg to find out.
-> *drv describes the drivetrain of the vehicle (f, r, 4)*

4. Make a scatterplot of hwy vs cyl.
```{r}
ggplot(data = mpg) +
  geom_point(aes(x = cyl, y = hwy))
```

5. What happens if you make a scatterplot of class vs drv? Why is the plot not useful?
-> *This plot will run, but it is not useful because it is comparing two categorical variables.*

### Exercises pg. 12

1. What’s gone wrong with this code? Why are the points not blue?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))
```
-> *The points are not blue because color = "blue" is inside the geom_point() aesthetic when it should be outside.*

2. Which variables in mpg are categorical? Which variables are continuous? (Hint: type ?mpg to read the documentation for the dataset). How can you see this information when you run mpg?
-> *Categorical: manufacturer model, year, cyl, trans, drv, fl, class*
-> *Continuous: displ, cty, hwy*

3. Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical vs. continuous variables?
```{r}
ggplot(mpg, aes(x = city, y = hwy)) + 
  geom_point(aes(size = class, color = class))

ggplot(mpg, aes(x = displ, y = hwy)) + 
  geom_point(aes(color = hwy))
```
-> *Categorical:* If you map color onto a categorical variable, each gets its own discrete color
-> *Continous:* If you map color onto a continuous variable, a color spectrum is created

4. What happens if you map the same variable to multiple aesthetics?
-> *Those aesthetics are all mapped*

5. What does the stroke aesthetic do? What shapes does it work with? (Hint: use ?geom_point)
```{r}
ggplot(mpg, aes(x = displ, y = hwy)) + 
  geom_point(aes(stroke = displ, color = trans))
```

-> *The stroke aesthetic changes the border around the points*

6. What happens if you map an aesthetic to something other than a variable name, like aes(colour = displ < 5)? Note, you’ll also need to specify x and y.
```{r}
ggplot(mpg, aes(x = displ, y = hwy)) + 
  geom_point(aes(color = displ < 5))
```
-> *It will just color the points as specified by the color aes.*

### Exercises pg. 15

1. What happens if you facet on a continuous variable?
-> *This makes no sense, don't do this.*

2. What do the empty cells in plot with facet_grid(drv ~ cyl) mean? How do they relate to this plot?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = drv, y = cyl)) +
  facet_grid(drv ~ cyl)
```
-> *There are no vehicles that have that a combination of 4wd and 5 cylinders, rwd and 4 cylinders, or rwd and 5 cylinders.*

3. What plots does the following code make? What does . do?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)
```
-> *. flips the facets on their sides?*

4. Take the first faceted plot in this section. What are the advantages to using faceting instead of the colour aesthetic? What are the disadvantages? How might the balance change if you had a larger dataset?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
```
-> *Facets can make it much easier to see trends for each categorical variable, rather than plotting all variables together and color-coding. However, it can become overwhelming to facet if you have a very large dataset with many variables.*

5. Read ?facet_wrap. What does nrow do? What does ncol do? What other options control the layout of the individual panels? Why doesn’t facet_grid() have nrow and ncol arguments?
-> *nrow and ncol specifies the number of rows and columns in a faceted plot.*

6. When using facet_grid() you should usually put the variable with more unique levels in the columns. Why?
-> *I don't know...*

### Exercises pg. 20

1. What geom would you use to draw a line chart? A boxplot? A histogram? An area chart?
-> *geom_line, geom_boxplot, geom_histgram, geom_area*

2. Run this code in your head and predict what the output will look like. Then, run the code in R and check your predictions.
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = FALSE)

ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(aes(color = drv)) + 
  geom_smooth(se = FALSE)
```

3. What does show.legend = FALSE do? What happens if you remove it?
Why do you think I used it earlier in the chapter?
-> *show.legend = FALSE removes the legend from the plot. If you remove this, the legend will print.*

4. What does the se argument to geom_smooth() do?
-> *se creats a standard error ribbon around the line fit to the data.*

5. Will these two graphs look different? Why/why not?
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth()

ggplot() + 
  geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))
```
-> *These two plots are the same. The first specifies the global aesthetics (which apply to all geoms), whereas the second specifies the same aesthetics for each geom.*

6. Recreate the R code necessary to generate the following graphs.
```{r}
# a
ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point() +
  geom_smooth(se = FALSE)

# b 
ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point() +
  geom_smooth(aes(group = drv), se = FALSE)

# c 
ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point(aes(col = drv)) +
  geom_smooth(aes(group = drv, col = drv), se = FALSE)

# d
ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point(aes(col = drv)) +
  geom_smooth(se = FALSE)

# e
ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point(aes(col = drv)) +
  geom_smooth(aes(group = drv, lty = drv), se = FALSE)

# f
ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point(aes(col = drv)) 
```

### Exercises pg. 26

1. What is the default geom associated with stat_summary()? How could you rewrite the previous plot to use that geom function instead of the stat function?
```{r}
ggplot(data = diamonds, aes(x = cut, y = depth)) +
  geom_line() # CAN'T FIGURE THIS OUT
```
-> *geom_bar*

2. What does geom_col() do? How is it different to geom_bar()?
-> *geom_col() creates a plot of the raw data, whereas geom_bar() computes a summary statistic to plot.*

3. Most geoms and stats come in pairs that are almost always used in concert. Read through the documentation and make a list of all the pairs. What do they have in common?
-> *I don't feel like writing these out so just look them up.*

4. What variables does stat_smooth() compute? What parameters control its behaviour?
-> *?*

5. In our proportion bar chart, we need to set group = 1. Why? In other words what is the problem with these two graphs?
```{r}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, y = ..prop..))
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, fill = color, y = ..prop..))
```
-> *Setting group = 1 means that all bars will add to 1.*

### Exercises pg. 31

1. What is the problem with this plot? How could you improve it?
```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point()
```
-> *The overlapping points should be jittered.*

2. What parameters to geom_jitter() control the amount of jittering?
-> *height and width*

3. Compare and contrast geom_jitter() with geom_count().
```{r}
ggplot(mpg, aes(x = cty, y = hwy)) +
  geom_jitter() # spreads out the observations

ggplot(mpg, aes(x = cty, y = hwy)) +
  geom_count() # gives number of obs as the size of the point
```

4. What’s the default position adjustment for geom_boxplot()? Create a visualisation of the mpg dataset that demonstrates it.
-> *position = "dodge2"*

### Exercises pg. 33

1. Turn a stacked bar chart into a pie chart using coord_polar().
```{r}
ggplot(diamonds, aes(x = cut, fill = cut)) +
  geom_bar() +
  coord_polar() 
```

2. What does labs() do? Read the documentation.
-> *labs() allows you to specify the x and y label names*

3. What’s the difference between coord_quickmap() and coord_map()?
-> *coord_quickmap() uses the mercator projection, whereas coord_quickmap is a quick approximation that does preserve straight lines. It works best for smaller areas closer to the equator.*

4. What does the plot below tell you about the relationship between city and highway mpg? Why is coord_fixed() important? What does geom_abline() do?
```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  geom_abline() +
  coord_fixed()
```
-> *Default coord_fixed() ensures that one unit on the x-axis is the same length as one unit on the y-axis. geom_abline shows you the hypothetical 1:1 ratio of your two variables.*

