---
title: "Ch20_Many_Models_with_purrr_and_broom"
author: "Sam Csik"
date: "4/16/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Exercises pg. 409 (25.2.5)

1. A linear trend seems to be slightly too simple for the overall trend. Can you do better with a quadratic polynomial? How can you interpret the coefficients of the quadratic? (Hint you might want to transform year so that it has mean zero.)

2. Explore other methods for visualising the distribution of R^2^ per continent. You might want to try the `ggbeeswarm` package, which provides similar methods for avoiding overlaps as jitter, but uses deterministic methods.

3. To create the last plot (showing the data for the countries with the worst model fits), we needed two steps: we created a data frame with one row per country and then semi-joined it to the original dataset. It’s possible to avoid this join if we use `unnest()` instead of `unnest(.drop = TRUE)`. How?

### Exercises pg. 415 (25.4.5)

1. List all the functions that you can think of that take a atomic vector and return a list.

2. Brainstorm useful summary functions that, like `quantile()`, return multiple values.

3. What’s missing in the following data frame? How does `quantile()` return that missing piece? Why isn’t that helpful here?
```{r}
mtcars %>% 
  group_by(cyl) %>% 
  summarise(q = list(quantile(mpg))) %>% 
  unnest()
#> # A tibble: 15 x 2
#>     cyl     q
#>   <dbl> <dbl>
#> 1     4  21.4
#> 2     4  22.8
#> 3     4  26  
#> 4     4  30.4
#> 5     4  33.9
#> 6     6  17.8
#> # … with 9 more rows
```

### Exercises pg. 419 (25.5.3)

1. Why might the `lengths()` function be useful for creating atomic vector columns from list-columns?

2. List the most common types of vector found in a data frame. What makes lists different?

