---
title: "Ch3_Data_Transformation_with_dplyr"
author: "Sam Csik"
date: "4/9/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Load required packages
```{r}
library(nycflights13)
library(tidyverse)
```

### Exercises pg. 49

1. Find all flights that

  a. Had an arrival delay of two or more hours
  b. Flew to Houston (IAH or HOU)
  c. Were operated by United, American, or Delta
  d. Departed in summer (July, August, and September)
  e. Arrived more than two hours late, but didn’t leave late
  f. Were delayed by at least an hour, but made up over 30 minutes in flight
  g. Departed between midnight and 6am (inclusive)
```{r}

```

2. Another useful dplyr filtering helper is between(). What does it do? Can you use it to simplify the code needed to answer the previous challenges?
```{r}

```

3. How many flights have a missing dep_time? What other variables are missing? What might these rows represent?
```{r}

```

4. Why is NA ^ 0 not missing? Why is NA | TRUE not missing? Why is FALSE & NA not missing? Can you figure out the general rule? (NA * 0 is a tricky counterexample!)
```{r}

```

### Exercises pg. 54

1. Brainstorm as many ways as possible to select dep_time, dep_delay, arr_time, and arr_delay from flights.

2. What happens if you include the name of a variable multiple times in a select() call?

3. What does the one_of() function do? Why might it be helpful in conjunction with this vector?
```{r}
vars <- c("year", "month", "day", "dep_delay", "arr_delay")
```

4. Does the result of running the following code surprise you? How do the select helpers deal with case by default? How can you change that default?
```{r}
select(flights, contains("TIME"))
```



