---
title: "Ch7_Tibbles_with_Tibble"
author: "Sam Csik"
date: "4/15/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Exercises pg. 123 (10.5)

1. How can you tell if an object is a tibble? (Hint: try printing mtcars, which is a regular data frame).

2. Compare and contrast the following operations on a data.frame and equivalent tibble. What is different? Why might the default data frame behaviours cause you frustration?
```{r}
df <- data.frame(abc = 1, xyz = "a")
df$x
df[, "xyz"]
df[, c("abc", "xyz")]
```

3. If you have the name of a variable stored in an object, e.g. var <- "mpg", how can you extract the reference variable from a tibble?

4. Practice referring to non-syntactic names in the following data frame by:

  a. Extracting the variable called 1.
  b.  Plotting a scatterplot of 1 vs 2.
  c. Creating a new column called 3 which is 2 divided by 1.
  d.  Renaming the columns to one, two and three.
  
```{r}
annoying <- tibble(
  `1` = 1:10,
  `2` = `1` * 2 + rnorm(length(`1`))
)
```

5. What does tibble::enframe() do? When might you use it?

6. What option controls how many additional column names are printed at the footer of a tibble?
