---
title: "Ch9_Tidy_Data_with_tidyr"
author: "Sam Csik"
date: "4/15/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Exercises pg. 151 (12.2.1)

1. Using prose, describe how the variables and observations are organised in each of the sample tables.

2. Compute the rate for table2, and table4a + table4b. You will need to perform four operations:

  a. Extract the number of TB cases per country per year.
  b. Extract the matching population per country per year.
  c. Divide cases by population, and multiply by 10000.
  d. Store back in the appropriate place.
  3. Which representation is easiest to work with? Which is hardest? Why?

3. Recreate the plot showing change in cases over time using table2 instead of table1. What do you need to do first?

### Exercises pg. 156 (12.3.3)

1. Why are gather() and spread() not perfectly symmetrical?
Carefully consider the following example:
```{r}
stocks <- tibble(
  year   = c(2015, 2015, 2016, 2016),
  half  = c(   1,    2,     1,    2),
  return = c(1.88, 0.59, 0.92, 0.17)
)
stocks %>% 
  spread(year, return) %>% 
  gather("year", "return", `2015`:`2016`)
```
(Hint: look at the variable types and think about column names.)

2. Both spread() and gather() have a convert argument. What does it do?

3. Why does this code fail?
```{r}
table4a %>% 
  gather(1999, 2000, key = "year", value = "cases")
#> Error in inds_combine(.vars, ind_list): Position must be between 0 and n
```

4. Why does spreading this tibble fail? How could you add a new column to fix the problem?
```{r}
people <- tribble(
  ~name,             ~key,    ~value,
  #-----------------|--------|------
  "Phillip Woods",   "age",       45,
  "Phillip Woods",   "height",   186,
  "Phillip Woods",   "age",       50,
  "Jessica Cordero", "age",       37,
  "Jessica Cordero", "height",   156
)
```

5. Tidy the simple tibble below. Do you need to spread or gather it? What are the variables?
```{r}
preg <- tribble(
  ~pregnant, ~male, ~female,
  "yes",     NA,    10,
  "no",      20,    12
)
```

### Exercises pg. 160 (12.4.3)

1. What do the extra and fill arguments do in separate()? Experiment with the various options for the following two toy datasets.
```{r}
tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three"))

tibble(x = c("a,b,c", "d,e", "f,g,i")) %>% 
  separate(x, c("one", "two", "three"))
```

2. Both unite() and separate() have a remove argument. What does it do? Why would you set it to FALSE?

3. Compare and contrast separate() and extract(). Why are there three variations of separation (by position, by separator, and with groups), but only one unite?

### Exercises pg. 163 (12.5.1)

1. Compare and contrast the `fil` arguments to `spread()` and `complete()`.

2. What does the direction arguement to `fill()` do?

### Exercises pg. 168 (12.1.6)

1. In this case study I set na.rm = TRUE just to make it easier to check that we had the correct values. Is this reasonable? Think about how missing values are represented in this dataset. Are there implicit missing values? What’s the difference between an NA and zero?

2. What happens if you neglect the `mutate()` step? `(mutate(key = stringr::str_replace(key, "newrel", "new_rel")))`

3. I claimed that iso2 and iso3 were redundant with country. Confirm this claim.

4. For each country, year, and sex compute the total number of cases of TB. Make an informative visualisation of the data.